### 2020-05-14 writeup/transfer.tex
sec 3.1

\subsection{Model Distance}

@@

\textbf{Example.}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
	For the task models, suppose that $\beta_t$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_s - \beta_t$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	We have $n = c \cdot p$ data points from each task.

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, assume that $c > 50$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac 1 4 \frac{(2c-1)^2}{(c-1)c^2} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{(2c-1)^2}{(c-1)c^2} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

We obtain the following insight from Proposition \ref{prop_dist_transition}.
First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
On the other hand, model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
Hence, the type of transfer is determined by the trade-off between the bias caused by model shift and the reduction of variance.

@@

\subsection{Data Ratio}

\subsection{Covariate Shift}

>>>>

\subsection{Task Model Similarities}

@@

\textbf{Example.}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, assume that $c > 100$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac 2 3 \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac 3 2 \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

The proof of Proposition \ref{prop_dist_transition} involves two parts.
First, adding the source task has a positive effect of reducing the variance of the estimator, which scales with $n_1 = c_1 p$, the number of source task data points.
Second, the difference between task models $\beta_1$ and $\beta_2$ introduces an additional bias term, which scales with $pd^2$, the distance between $\beta_1$ and $\beta_2$.
Hence, the type of transfer is determined by the trade-off between model shift bias and the reduction of variance.
The proof can be found in Appendix \ref{app_proof_31}, which is based on our main result described later in Theorem \ref{thm_model_shift}.

@@

\textbf{Implications.} \todo{add connection to tasksonomy}

\subsection{Data Efficiency}

\subsection{Covariance Alignment}
